Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-06-09 WSSSPE1_report/WSSSPE1_summary_report.tex
adding information about submission regions and domain/discipline in section 2

>>>>

The workshop received submissions from eight countries across the North
American and European regions. In some instances authors collaborated across
the US and European regions contributing jointly authored papers. A majority of
contributions came from the US with 42 papers where at least one author was
affiliated to a US institution. A total of 10 submissions were from the
European region and 4 were from Canada.

In terms of subject of the papers, the submissions were dominated by the domain
of practice of sustainable software engineering and management with about 32
papers based on these themes. These papers were further based on a variety of
disciplines including infrastructure and architecture, user engagement, and
governance. Additionally, 18 papers were based on the pure sciences and
applied mathematics domains with disciplines including High Energy Physics,
Bioinformatics, Nanotechnology, Chemistry, and material sciences. Others were
dominated by miscellaneous topics such as science gateways and visualization.
